Open-source tools in R for landscape ecology

### 2021-04-26 paper/paper.Rmd
Adding Where to Start Box

>>>>

\begin{tabularx}{1\textwidth}{|X|}
\hline
\multicolumn{1}{|c|}{\textbf{Box 1: Where to start}} \\

\\

\textbf{1.} Get familiar with basics of \textit{R} programming language. 
Good resources can be found at \url{https://cran.r-project.org/manuals.html}. \\

\textbf{2.} Understand the fundamental spatial data types i.e, raster data and vector data.
This also includes being able to process the data using the corresponding packages such as \textit{raster} or \textit{sf}. 
These packakage also have excellent documentation at \url{https://rspatial.org/raster} and \url{https://r-spatial.github.io/sf}, respectively. \\

\textbf{3.} Be able to transform coordinate reference systems of data from different sources. Depending on the data type, \textit{raster} or \textit{sf} and the corresponding documentations are good starting points. \\

\textbf{4.} Do a quick visualization of the data for inspection or a first glance at the data. 
This can be done with base \textit{R} or if already familiar \textit{ggplot2}. \\

\textbf{5.} Find suitable \textit{R} package for research questions. 
This can be difficult since research questions, available data and package are diverse. 
Good starting points are the CRAN Task Views (mainly \url{https://cran.r-project.org/web/views/Spatial.html}) or review papers similar to this one. 
If several packages exist, try all of them and see which ones suites the question and data the best. \\

\textbf{6.} Create publication-quality figures and maps using e.g. \textit{ggspatial} or \textit{tmap}. 
Help for both packages can be found on the corresponding homepages \url{https://paleolimbot.github.io/ggspatial/index.html} or \url{https://mtennekes.github.io/tmap}. \\

\textbf{7.} Make reproducible \textit{R} scripts publicly available if possible. \\

\textbf{8.} Further excellent resources with applied help about spatial data in \textit{R} can be found \url{https://keen-swartz-3146c4.netlify.app}, \url{https://rspatial.org}, or \url{https://geocompr.robinlovelace.net}. \\

\hline
\end{tabularx}
